Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2020-12-18 RJtemplate_gtsummary_submission.tex

\textbf{A note about notation:}
Throughout the \pkg{gtsummary} package, you'll find function arguments that accept a list of formulas (or a single formula) as the input.
In the example above, the label for the age variable was updated using \texttt{label = age $\sim$ "Patient Age"}---equivalently, \texttt{label = list(age $\sim$ "Patient Age")}.
To select groups of variables, utilize the select helpers from the tidyselect \citep{tidyselect} and \pkg{gtsummary}.
Above, \texttt{all\_continuous()} was utilized to change the summary statistics for all continuous variables. 
Similarly, users may utilize \texttt{all\_categorical()} (from \pkg{gtsummary}), or any of the tidyselect helpers used throughout the tidyverse \citep{tidyverse} package, such as \texttt{starts\_with()}, \texttt{contains()}, etc.

@@

\begin{example}
# create weighted survey object, keep only two counties
data(api, package = "survey")
svy_api <- 
  survey::svydesign(id = ~dnum, weights = ~pw, data = apiclus1, fpc = ~fpc) %>%
  subset(cname %in% c("Alameda", "Los Angeles"))

# summarize data
svy_api %>%
  tbl_svysummary(by = cname, 
                 include = c(growth, target, cname),
                 label = list(growth ~ "Growth",
                              target ~ "Target")) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.28]{svysummary.png}
  \centering
\end{figure}

@@

\begin{example}
trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%  
  add_overall() %>%    
  add_p() %>%      
  add_stat_label() %>%     
  modify_header(label ~ "**Variable**") %>%   
  modify_spanning_header(c(stat_1, stat_2) ~ "**Treatment Received**") %>%  
  as_gt() %>% 
  gt::tab_header(   
    title = gt::md("**Table 1. Patient Characteristics**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")   
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.28]{custom.png}
  \centering
\end{figure}

>>>>

\textbf{A note about notation:}
Throughout the \pkg{gtsummary} package, you'll find function arguments that accept a list of formulas (or a single formula) as the input.
In the example above, the label for the age variable was updated using \texttt{label = age $\sim$ "Patient Age"}---equivalently, \texttt{label = list(age $\sim$ "Patient Age")}.
To select groups of variables, utilize the select helpers from the tidyselect \citep{tidyselect} and \pkg{gtsummary}.
The \texttt{all\_continuous()} selector is a convenient way to select all continuous variables.
In the example above it could have been used to change the summary statistics for all continuous variables---\code{all\_continuous() ~ c("\{N\_nonmiss\}", "\{mean\} (\{sd\})")}. 
Similarly, users may utilize \texttt{all\_categorical()} (from \pkg{gtsummary}), or any of the tidyselect helpers used throughout the tidyverse \citep{tidyverse} package, such as \texttt{starts\_with()}, \texttt{contains()}, etc.

@@

\begin{example}
# convert trial data frame to survey object
svy_trial <- survey::svydesign(data = trial, ids = ~ 1, weights = ~ 1)

tbl_svysummary_1 <-
  svy_trial %>%
  tbl_svysummary(by = trt, include = c(trt, age, grade)) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.28]{svysummary.png}
  \centering
\end{figure}

@@

The example below includes customization using both gtsummary and gt functions.
The gtsummary functions are utilized to bold p-values below a threshold, bold the variable labels,  update the column header, and add a spanning header

\begin{example}
trial %>%
  select(age, grade, trt) %>%
tbl_summary(by = trt, missing = "no") %>%
  add_overall() %>%
  add_p() %>%
  add_q() %>%
  add_stat_label() %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  modify_header(label ~ "**Variable**") %>% 
  modify_spanning_header(c(stat_1, stat_2) ~ "**Treatment Received**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Patient Characteristics**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.28]{custom.png}
  \centering
\end{figure}
